### 2020-09-16 paper/natastron/paper.tex
Started results

\usepackage{chngcntr}
\usepackage{graphicx}
\graphicspath{ {Images/} }
\usepackage[symbol]{footmisc}

@@

Determining whether weakened magnetic braking is a true phenomenon or a bias in star spot observations requires new data, which can be provided by asteroseismology. A star's rotation causes modes of oscillation to split into multiplets, making it possible to measure the rate of rotation by measuring oscillation frequencies \cite{ledoux1951}. Asteroseismic rotation is more difficult to obtain than rotation from star spots, but does not require  spots to be visible, meaning that we can measure rotation for quiescent stars that would not have been present in existing catalogues of star-spot rotation. Previous studies have shown that asteroseismic rotation rates probe the near-surface of the star, making them comparable to spot rotation rates, and the perfect avenue to explore whether weakened magnetic braking truly takes place \cite{lund+2014, benomar+2015}. Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of colours and ages, and evaluate this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one where weakened magnetic braking takes place.

@@

In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) oscillations for each star, of which the latter have significantly lower signal-to noise. Radial oscillations ($\ell = 0$), which are also visible, do not split. In this work, we studied a sample of 94 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}.

For the purposes of studying gyrochronology, we wanted to be able to single out stars for which the loss of angular momentum via magnetized winds is the dominant source of rotational evolution. Stars with $T_{\rm eff} > 6250\, \rm{K}$ fall beyond the `Kraft' break, which roughly separate stars with large convective envelopes (at lower temperatures) from those with thin ones (high temperatures), at which the efficiency of angular momentum transport is greatly reduced.  We also wanted to single out stars that have started to evolve onto the sub-giant branch, where the outer envelope begins to expand, making them challenging targets for gyrochronology. While there are no identified mixed dipole modes\footnote{In evolved stars, gravity modes propagating in the radiative interior will interfere with non-radial p modes, changing their structure and creating so-called `mixed modes' \cite{bedding+2010}.} in the stars in our sample, indicating an evolved structure, we can still apply a conservative sub-giant classification of stars with $\rm{log(g)} < 4.0\, \rm dex$. \cite{garcia+2014}.

Our sample spans surface gravities of $3.8\, \rm{dex} < \rm{log(g)} < 4.6\, \rm{dex}$ and temperatures of $5000\, \rm{K} < T_{\rm eff} <  6700\, \rm{K}.$ Of our full sample of 95 targets, 67 stars fall in the range $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$, which we call main sequence (MS) stars. Four targets in our sample have $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$ which we class as potentially being sub-giants (SG stars). The remaining 24 stars in our sample have $T_{\rm eff} > 6250\, \rm K$, which we class as being hot main sequence stars.

%% reduce this to two paragraphs., point to Figure 1. Then go straigh to what we did and results. Then discussion with a plot per paragraph, and then copy and paste section 3.

\section{Results}
 Neither catalogues reported stellar rotation, so we repeated the mode frequency fitting with a model that accounted for this in more detail (see \textbf{\textit{Methods}}).

>>>>

\usepackage{chngcntr}
\usepackage{xspace}
\usepackage{graphicx}
\graphicspath{{Images/}}
\usepackage[symbol]{footmisc}

@@

Determining whether weakened magnetic braking is a true phenomenon or a bias in star spot observations requires new data, which can be provided by asteroseismology. A star's rotation causes modes of oscillation to split into multiplets, making it possible to measure the rate of rotation by measuring oscillation frequencies \cite{ledoux1951}. Asteroseismic rotation is more difficult to obtain than rotation from star spots, but does not require  spots to be visible, meaning that we can measure rotation for quiescent stars that would not have been present in existing catalogues of star-spot rotation. Previous studies have shown that asteroseismic rotation rates probe the near-surface of the star, making them comparable to spot rotation rates, and the perfect avenue to explore whether weakened magnetic braking truly takes place \cite{lund+2014, benomar+2015}. Here, we measured asteroseismic rotation rates of 91 main sequence stars across a broad range of colours and ages, and evaluate this new ensemble to determine whether it agrees more closely with a classical rotational evolution scenario, or one where weakened magnetic braking takes place.\\

@@

In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) oscillations for each star, of which the latter have significantly lower signal-to noise. Radial oscillations ($\ell = 0$), which are also visible, do not split. In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}. A table of parameters taken from these studies, as well as details on how these were obtained, can be found in \textbf{\textit{Methods}}.

We separated our sample into three categories \cite{garcia+2014}: 64 main sequence stars (MS, $\rm{log(g)} > 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$); 4 potential sub-giant stars (SG, $\rm{log(g)} < 4.0\, \rm dex$, $T_{\rm eff} < 6250\, \rm K$, which may have begun to evolve off the main sequence, complicating their rotational history\footnote{It should be noted that none of these stars have identified mixed dipole modes, which indicate an evolved structure (see \cite{bedding+2010}).}; and 24 `hot' stars (H, $T_{\rm eff} > 6250\, \rm K$), which lie above the Kraft break, the point at which convective envelopes are tenuous, and angular momentum loss becomes inefficient \cite{kraft1967}. The sample, which can be seen in Figure \ref{fig:sample}, spans surface gravities of $3.8\, \rm{dex} < \rm{log(g)} < 4.6\, \rm{dex}$, temperatures of $5000\, \textrm{K} < T_{\rm eff} <  6700\, \rm{K}$, and ages from $1$ to $\sim 13\, \rm{Gyr}$.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{data.pdf}
	\caption{Our sample of 95 stars from the Kages and LEGACY catalogues coloured by asteroseismic age  \cite{silvaaguirre+2015, silvaaguirre+2017}. The dashed lines indicate our classification boundaries: main sequence (circles, $\teff < 6250\, K$, $\logg < 4\, \rm{dex}$), potential sub-giants (squares, $\teff < 6250\, K$, $\logg > 4\, \rm{dex}$), and `hot' stars (triangles, $\teff > 6250\, K$). The Sun is shown with the `$\odot$' symbol, and has an age of $4.6\, \rm{Gyr}$ \cite{bonanno+frohlich2015
		}. The solid lines are evolutionary tracks generated using MESA \cite{paxton+2017}, for a metallicity of $Z = 0.01493$ and helium content of $Y = 0.26588$. Left to right, they represent masses of $1.5$, $1.25$, $1$ and $0.75\, M_\odot$. Vertical errorbars are too small to be visible.}
	\label{fig:sample}
\end{figure}

\section{Results}
 The `Kages' and LEGACY catalogues that form our stellar sample both performed detailed asteroseismic frequency fitting, but did not report asteroseismic rotation. Here, we repeated the mode frequency fitting with an improved Bayesian model that accounted for rotation in more detail (see \textbf{\textit{Methods}}). We fit our model to \kepler power-spectra of 95 stars, which was successful in 94 cases. We compared our results with both published and unpublished asteroseismic rotation rates, and found that the three stars with the lowest angles of inclination ($< 10^\circ$) were inconsistent with previous work. To some degree this was expected, as  for stars viewed near pole-on the power of the split modes of oscillation are extremely small. We flagged our rotation rates for these stars, and did not use them in the next steps in our analysis, leaving a sample of 91 stars for which we judge our asteroseismic rotation measurements to be robust (for a full justification, see \textit{\textbf{Methods}}).
